LAGOS lake depth

### 2020-02-14 figures/01_geometry.Rmd
compare slopes with a heatmap

```{r }
# compare inlake slope against buffer slope

>>>>

```{r slope-compare, echo=FALSE, message=FALSE, eval=FALSE, warning=FALSE, results='hide'}
# compare inlake slope, buffer slope, and online slope
# setwd("figures") 
bp <- readRDS("../data/00_bathy_depth/bathy_pnts.rds")
dt <- read.csv("../data/00_geometry/nearshore.csv", stringsAsFactors = FALSE) %>%
  mutate(llid = as.character(llid))
dt <- left_join(dt, st_drop_geometry(bp), 
                by = "llid") %>%
  dplyr::filter(!is.na(inlake_slope_mean))

jsta::jheatmap(dt)
jsta::jheatmap(
  dplyr::select(dt, 
                slope_online_mean,
                inlake_slope_mean,
                slope_mean, 
                slope_mean_ne,
                dist_deepest, 
                dist_viscenter, 
                maxdepth,
                meandepth))

plot(dt$inlake_slope_mean, dt$slope_online_mean)
plot(dt$inlake_slope_mean, dt$slope_mean)
plot(dt$inlake_slope_mean, dt$slope_mean_ne)
plot(dt$slope_mean, dt$slope_mean_ne)
dt$res_elev_1
plot(dt$inlake_slope_median, dt$slope_online_median)

plot(dt$inlake_slope, dt$slope_mean_ne)
plot(dt$inlake_slope, dt$slope_online)
plot(dt$slope_mean, dt$slope_mean_ne)
